Data Aggregation System - a system for information retrieval on demand over relational and non-relational distributed data sources

### 2011-03-16 doc/chep_paper/das_chep2010_proceedings.tex
Update DAS CHEP paper with comments provided by referees
Signed-off-by: Valentin Kuznetsov <vkuznet@gmail.com>


git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@11969 4525493e-7705-40b1-a816-d608a930855b

The architecture of DAS was designed as a series of independent components, which can scale from all running on a single node to multiple nodes and duplicate components, as necessary (Fig.~\ref{dasarch}). An initial description of the architectur, choice of technology and comparison with similar systems was given in \cite{das2010}. Here we present further development of the query language (Sec.~\ref{dasql}), analytics (Sec.~\ref{analytics}) and initial benchmark results (Sec.~\ref{benchmarks}).

@@

Testing was performed with the cache pre-populated with approximately $5\times10^7$ records (100 times the expected volume), consisting of \emph{block} records from the CMS PhEDEx~\cite{phedex} and DBS systems. We test with up to 500 clients making requests in parallel. Each client requests one random record from the entire result set (which will test the time required for DAS to process the query but largely exclude the time required to serialise a large output set), using queries of the form \verb block=/[a-z]* (past experience with the DBS system shows wildcard queries are very common, even when the user knows the complete string in question). Fig.~\ref{dasbench} shows the benchmark results.

>>>>

The architecture of DAS was designed as a series of independent components, which can scale from all running on a single node to multiple nodes and duplicate components, as necessary (Fig.~\ref{dasarch}). An initial description of the architecture, choice of technology and comparison with similar systems was given in \cite{das2010}. Here we present further development of the query language (Sec.~\ref{dasql}), analytics (Sec.~\ref{analytics}) and initial benchmark results (Sec.~\ref{benchmarks}).

@@

%Testing was performed with the cache pre-populated with approximately $5\times10^7$ records (100 times the expected volume), consisting of \emph{block} records from the CMS PhEDEx~\cite{phedex} and DBS systems. We test with up to 500 clients making requests in parallel. Each client requests one random record from the entire result set (which will test the time required for DAS to process the query but largely exclude the time required to serialise a large output set), using queries of the form \verb block=/[a-z]* (past experience with the DBS system shows wildcard queries are very common, even when the user knows the complete string in question). Fig.~\ref{dasbench} shows the benchmark results.
Testing was performed with the cache pre-populated with approximately 
$5\times10^7$ records (100 times the expected volume), consisting 
of \emph{block} records from the CMS PhEDEx~\cite{phedex} and DBS 
systems. Each \emph{block} record is a JSON document with common keys, such as
\emph{name, nevents, nfiles, replica}, etc.
We test with up to 500 clients making requests in parallel. 
Each client requests a random wildcard query, e.g. \verb block=/a* , and fetches one random
record from the returned set (which will test the time required for DAS to parse the 
query and access the cache but largely exclude the time required to serialise a large 
output set). No additional operations were done during this step.
Fig.~\ref{dasbench} shows the benchmark results.
